---
title: "Problem Set 2"
output: html_notebook
---

First, I will set up my workspace
```{r}
rm(list = ls())
library(here)
library(ggplot2)
library(tidyverse)
```

Now, I will read my data into my workspace
```{r}
DF <- read.csv(here("Data", "Halloween_data_PS2.csv"))
```

Now I want to get a quick idea of the varialbes/variable types in my dataset
```{r}
glimpse(DF) #I can see that Costume and Type are both listed as character variables, I will change them to factors
```

I will change Costume and Type to factors
```{r}
DF$Costume <- as.factor(DF$Costume)  #convert character column to factor

DF$Type <- as.factor(DF$Type)

class(DF$Costume)
class(DF$Type) #both the Costume and Type variables have been converted to factors!
```


Now, I want to look a little closer at my dataset. 
```{r}
str(DF) #I can see that there are 15 levels in the Costume variable, and 4 levels in the Type variable
```

Let's see what the levels of Costume are
```{r}
levels(DF$Costume) #Hmm, I see some duplicate entries (eg different capitalizations of Wonder woman, Wonder Woman, and wonder woman). R thinks these are different things
```

Now I will fix the data entries so the format for spelling/capitalization is consistent for each level
```{r}

```


