---
title: "Problem Set 2"
output: html_notebook
---

First, I will set up my workspace
```{r}
rm(list = ls())
library(here)
library(ggplot2)
library(tidyverse)
```

Now, I will read my data into my workspace
```{r}
DF <- read.csv(here("Data", "Halloween_data_PS2.csv"))
```

Now I want to get a quick idea of the varialbes/variable types in my dataset
```{r}
glimpse(DF) #I can see that Costume and Type are both listed as character variables, I will change them to factors
```

I will change Costume and Type to factors
```{r}
DF$Costume <- as.factor(DF$Costume)  #convert character column to factor

DF$Type <- as.factor(DF$Type)

class(DF$Costume)
class(DF$Type) #both the Costume and Type variables have been converted to factors!
```


Now, I want to look a little closer at my dataset. 
```{r}
str(DF) #I can see that there are 15 levels in the Costume variable, and 4 levels in the Type variable
```

Let's see what the levels of Costume are
```{r}
levels(DF$Costume) #Hmm, I see some duplicate entries (eg different capitalizations of Wonder woman, Wonder Woman, and wonder woman). R thinks these are different things
```

Now I will fix the data entries so the format for spelling/capitalization is consistent for each level
```{r}
#first I will fix the clowns
fix <- which(DF$Costume == "creepy clown" | DF$Costume == "clown") #tell R that "creepy clown" and "clown" are wrong

DF$Costume[fix]<- "Creepy clown" #assign the wrong versions to "Creepy clown"
```

```{r}
#now I will fix the witches
repair <- which(DF$Costume == "Witch" | DF$Costume == "witch ") #tell R that "Witch" and "witch " (space after the word) are wrong

DF$Costume[repair]<- "witch" #assign the wrong versions to "witch"
```

```{r}
#lastly, I will fix the Wonder Woman entries
better <- which(DF$Costume == "Wonder woman" | DF$Costume == "wonder woman") #tell R that "Wonder woman" and "wonder woman" are wrong

DF$Costume[better]<- "Wonder Woman" #assign the wrong versions to "Wonder Woman"
```

Now I want to check how many levels are in Costume to make sure my data repair steps worked
```{r}
unique(DF$Costume) #I can see that my repairs worked (even though R still "remembers" the old versions)
```


Let's check the levels of Type as well
```{r}
levels(DF$Type) #Looks like there's some mistakes
```

Now I will fix the capitalization issues in the Type variablce
```{r}
good <- which(DF$Type == "scary" | DF$Type == "scary ") #tell R that "scary" and "scary " are wrong

DF$Type[good]<- "Scary" #assin the wrong versions to "Scary"
```

And now I'll check to make sure my fix worked
```{r}
unique(DF$Type) #looks good! 
```


Now I want to calculate the mean age of trick-or-treaters and mean number of pieces of candy taken by Costume and Type 
```{r}
By_type <- DF %>% 
  group_by(Costume, Type) %>%
  summarize(num_pieces = mean(candy_pieces, na.rm = T),
            mean_age = mean(age, na.rm = T)) 
#I'm choosing to omit the NA's from the calculation so I can calculate means
```

Now I want to create a figure from this summarized dataset (that replicated Figure 1)
```{r}
#I will make a scatterplot
ggplot(By_type, aes(x = mean_age, y = num_pieces, 
                    color = Type)) +
  geom_point() +
  xlab("Mean age of kid (years)") +
  ylab("Mean number pieces taken") +
  theme_bw() +
  labs(caption = "Figure 1. Mean number of pieces of candy taken as a function of age of trick-or-treater and costume type (Red dots = costumes 
that are not scary; blue dots = scary costumes).") +
  theme(plot.caption = element_text(hjust = 0))
```

Next I will write code that isolates the data for children in “not scary” costumes who are 10 years old or younger
```{r}
Not_scary <- DF %>%
  filter(Type == "Not scary") %>%
  filter(age <= 10)
```

Now I will use the filtered data from above to plot a histogram showing the number of kids in each age class (replicating Figure 2)
```{r}
ggplot(Not_scary, aes(x = age)) +
  geom_histogram(bins = 4) +
  xlab("Age of child") +
  ylab("Number") +
  labs(caption = "Figure 2. Number of children age 10 and under wearing costumes that are not scary.") +
  theme(plot.caption = element_text(hjust = 0))

```


Next, I will write code that replicates figure 3 
```{r}
ggplot(DF, aes(x = Costume, y = age)) +
  geom_boxplot() +
  geom_point(size = 4, color = 'lightgrey', alpha = 0.7) + 
  facet_wrap(~ Type, ncol = 2) +
  xlab("Child age (years)") +
  ylab("Costume choice") +
  coord_flip()
```



